\chapterwithauthor{Máirín Duffy Strode}{Don't Be Shy}
					不要害羞

*					作者介绍
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*

\authorbio{Máirín Duffy Strode has been using Free and Open Source software since she
	   从高中至今，Máirín Duffy Strode一直使用着免费并且开源的软件，
was in high school, and has been a contributor for the past 8 years. She is involved
		    并且她在过去的8年中，为FOSS的发展做出了极大的贡献。她的工作涉及到
in both the Fedora and GNOME communities and has worked on interaction design,
Feaora（一个FOSS的Linux操作系统，附带百度百科http://baike.baidu.com/view/182182.htm）
	和GNOME
(一款FOSS的多平台应用软件，百度百科http://baike.baidu.com/view/281766.htm)，
						并且已经在社交设计、品牌化、肖像学的一些
branding, and/or iconography for a number of prominent FOSS applications such as
					优秀的FOSS软件上进行应用，比如Spacewalk（Spacewalk 是一个Linux和Solaris的系统管理解决方案。官方网址http://spacewalk.redhat.com/）、
Spacewalk, Anaconda, virt-manager, SELinux and SSSD. She has also been involved
Anaconda（Anaconda是Red Hat Linux和Fedora的安装管理程序。它以Python及C语言写成，以图形的PyGTK和文字的python-newt接口写成。它可以用来自动安装配置，使用户能够以最小的监督运行。百度百科地址http://baike.baidu.com/view/1491084.htm#7）、virt-manager（一个管理虚拟机的软件官方地址http://virt-manager.et.redhat.com/）、SELinux（SELinux(Security-Enhanced Linux) 是美国国家安全局（NSA）对于强制访问控制的实现，是 Linux? 上最杰出的新安全子系统。百度百科地址http://baike.baidu.com/view/487687.htm）和SSSD。			她
in outreach efforts teaching children design skills using FOSS tools such as
她也致力于在孩子中推广使用FOSS软件，比如说GIMP（GIMP 是 GNU 图像处理程序(GNU Image Manipulation Program)的缩写。包括几乎所有图象处理所需的功能，号称Linux下的PhotoShop。百度百科地址http://baike.baidu.com/view/8482.htm，官方网站www.gimp.org）和Inkscape（Inkscape是开源的矢量图形编辑软件，百度百科地址http://baike.baidu.com/view/1267893.htm，官方网站inkscape.org），努力倡导一场使用这些软件的运动
GIMP and Inkscape and is a fierce advocate for said tools. She is the team lead
							她是Fodera设计小组的领导人，还是
of the Fedora Design Team and a senior interaction designer with Red Hat, Inc.}
Red Hat（Red Hat是全球最大的开源技术厂家，其产品Red Hat Linux也是全世界应用最广泛的Linux。百度百科地址http://baike.baidu.com/view/1139590.htm，官方网址www.redhat.com）的一个高级互动的设计师。
\noindent{}I knew about and used Free and Open Source software for a long time before I
	在我成为一个FOSS软件的贡献者以前，我已经接触并且使用它们很长一段时间了。
became a contributor. This was not for lack of trying -- there were a couple of
			这不是因为缺少尝试，很多时候，失败是因为我太害羞并且害怕
false starts, and I succumbed to them mostly out of being too shy and afraid to
这么做
push through them. From the aftermath of those false starts and also from
			从这些失败以及FOSS项目中别的合伙人中，		
on-boarding other designers in FOSS projects, I have five tips to offer to you
						我有5点小建议给你，如果你想成为一个
as a designer trying to ramp up as a FOSS contributor:
FOSS的参与者。

\section*{1. Know that you are needed and wanted (badly!)}
	1.知道你需要和想要(迫切的)什么
My first false start happened when I was a first-year computer science student
我的第一次失败是在我只是一个伦斯勒理工学院的一年级新生的时候
at Rensselaer Polytechnic Institute. There was a particular project I used a lot
					那时有个我曾经使用并且想要参与的公共项目
and I wanted to get involved with it. I did not know anyone in the project (or
					我不认识这个项目里的任何人（或者说参与免费软件的任何人）
anyone who was involved in free software) so I was trying to get involved pretty
					但是我还是打算加入。
cold. The project's website indicated that they wanted help and that they had an
	这个项目的网站上表示他们需要帮助，并且他们有个网络聊天频道
IRC channel, so I lurked in there for a week or two. One day after a lull in
	于是我在那潜伏了一两个星期。			在某一天的会议的短暂的停顿中
conversation, I spoke up: I said I was a computer science student interested in
		我说：我是一个电脑科学的学生，对你们的这个项目很感兴趣，我想要加入你们。
usability and that I would love to get involved.

``Go away'' was the response. Furthermore, I was told that \emph{my} help was not
他们回答我的是：走开。		从那以后，我知道：帮助不是需要或者想要就能得到的。
needed nor wanted. 

This set me back a few years in getting involved -- just a few harsh words on IRC
这让我参与项目的激情退到了最低的位置――仅仅是网络聊天室中的一些苛刻的言语就让我害怕再尝试几乎5年之久。
made me afraid to try again for almost 5 years.  I did not discover until much
						直到很久以后的一个，我才被一个
later that the person who had essentially chased me out of that project's IRC
把我踢出那个聊天室的人在这个项目的边缘发现，然后发生了一系列的事，
channel was on the fringes of the project and had a long history of such

behavior, and that I really had not done anything wrong. If I had only kept
	尽管我什么也没做错。		如果当时我一直尝试，并且和其他人交流，
trying and talked to other people, I may have been able to get started back
我也许已经开始做这个项目了。
then.

If you would like to contribute to Free and Open Source software I guarantee you
如果你真的喜欢为FOSS软件做出贡献，我保证这边有个项目会需要你的参与。尤其你有着设计意识。
there is a project out there that really needs your help, especially if you are

design-minded! Are you into web design? Iconography? Usability? Skinning? UI
		你尝试过网页设计吗？知道影像学吗？了解什么是可用性吗？（译者表示Skinning是什么不知道了）
mockups? I have spoken to many FOSS developers who are not only desperate for
明白什么交做UI实体模型吗？我曾经询问过很多FOSS开发者，他们都表示需要这些专业性的人员
this kind of help, but who would also deeply appreciate it and love you to
来帮助开发，如果你又这些技能，他们将会非常乐意寻求你的帮助。
pieces for providing it.

If you encounter some initial resistance when first trying to get started with a
如果你在第一次开始一个项目之前，遭遇了一些阻碍，不要立刻放弃，不要像我一样。
project, learn from my experience and do not give up right away. If that project
								如果你觉得那个项目和你
turns out to not be right for you, though, do not worry and move on. Chances are,
想象中的不一样，别着急，继续做下去。					机会就在那边，
you are going to find a project you love that loves you back.
你会找到一个你喜欢的并且需要你的项目的。

\section*{2. Help the project help you help them}
		2.帮助这个项目，帮助你，帮助他们
Many Free and Open Source Software projects today are dominated by programmers and
现在的很多FOSS项目由程序员和工程师占主导地位，其中的一些非常的幸运，能够有着一个或者两个
engineers and while some are lucky enough to have the involvement of a creative
创作人员，对大多数项目来说，一个设计师，艺术家或者其它创作人员是一个遥不可及的梦想。
person or two, for most projects a designer, artist, or other creative's

presence is an often-yearned-for-yet-never-realized dream. In other words, even
								换句话说，尽管他们知道他们
though they understand they need your skills, they may not know what kinds of
需要你的能力，但是他们不知道如何向你寻求这个帮助，不知道什么样的信息他们需要给你，
help they can ask you for, what information they need to give you to be
甚至不知道如何才能和你有效的一起工作.
productive, or even the basics of how to work with you effectively. 

When I first started getting involved in various FOSS projects, I encountered
当我第一次开始参与不同的FOSS项目后，我遇到很多开发者，他们从来没有直接和一个设计师一起
many developers who had never worked directly with a designer before. At first,
工作过。								起初，我感到自己非常	
I felt pretty useless. I could not follow all of their conversation on IRC
没用。我跟不上他们在网络聊天室里面的对话，因为他们的谈话涉及到内部技术细节，而这些
because they involved technical details about backend pieces I was not familiar
是我不擅长的。
with. When they bothered to pay attention to me, they asked questions like,
	当他们感到困惑，然后把注意力转向我后，他们问了一些问题，就像“这里该用什么颜色？”
``What color should I put here?'' or ``What font should I use?'' What I really
或者“哪种字体比较好？”作为一个交互设计师，我真正想做的是达到这个项目的需求，而不是这些。
wanted as an interaction designer was to be privy to decision-making about how

to approach the requirements for the project. If a user needed a particular
						如果一个用户需要一个特别的功能，					
feature, I wanted to have a say in its design -- but I did not know when or where those decisions were happening and I felt shut out.
我会需要这个功能的一个详细的描述――但是我不知道什么时候或者是哪里应该怎么做，我觉得糟透了。
Design contains a pretty wide range of skills (illustration, typography,
设计需要品种繁多的技能（插图、排版、交互设计、视觉设计、图标设计、平面设计、
interaction design, visual design, icon design, graphic design, wordsmithing,
词汇甄别等）
etc.) and any given designer likely does not possess all of them. It is
并且很多设计师不会所有的这些技能。					这很容易
understandable, then, that a developer might not be sure what to ask you for.
理解，一个开发者不确定能够问你什么。
It is not that they are trying to shut you out -- they just do not know how you
这不是他们要把你拒之门外――他们只是不知道你需要或者想要什么而已。
need or want to be involved.

Help them help you. Make it clear to them the kind of work you would like to offer by providing samples of 
 帮助他们就是在帮助你。用一些列子让他们明白你能做什么。
other work you have done. Let them know what you need so											让他们知道你需要什么，这样他们
they can better understand how to help you engage in their project. For example -- when you first get involved in a particular initiative for the project, take the 
才会明白如何在这个项目里帮助你。					举个例子――当你第一次主动参与这个项目时，拿出它的设计大纲
time to outline the design process for it, and post it on the main development list so other contributors can follow along. If you need input at particular points in 						并且把它放到主要开发列表里，以便其它参与者能够遵从它。				在这过程中，如果你在某一个点要获得一个
the process, flag those points in your outline. If you are not sure how particular things happen -- such as the process for developing a new feature -- approach 
特别的输入，在你的大纲中标出这些点。		如果你无法确定那些特别的事会发生――就好像发展一些新特点的过程一样――问问那些非专业人士，让他们帮助你想出来。
someone on the side and ask them to walk you through it. If someone asks you to do something beyond your technical ability -- working with version-control, for example
							如果有人让你做一些超过你能力范围只能的事――比如说使用版本控制――或者你不喜欢这么干，直接说出来
 -- and you are not comfortable with that, say so.

Communicating your process and needs will prevent the project from having to
在开发过程中，和其它成员交流你的过程和需求，这样才会发挥出你的全部天赋。
make guesses and instead they will be able to make the best use of your talents.

\section*{3. Ask questions. Lots of questions. There are no stupid questions.}
		3.问问题，一大堆的问题，没有一个问题是不必要的
We have noticed sometimes in Fedora that when new designers come on board, they
在进行Fedora这个项目时，我们注意到新的设计师参与进来后，他们害怕问一些技术问题，
are afraid to ask technical questions for fear they will look stupid. 
因为他们认为这会让他们看起来很蠢。
The secret is, developers can be so specialized that there are a lot of
开发人员需要有着专门的知识，因为有着很多很多的技术细节超出了他们的专业知识，
technical details outside of their immediate expertise that they do not
有些他们无法理解甚至听都没听到过
understand either -- this happens even within the same project. The difference is that they are not afraid 
		――不管项目大小，总是会发生这样的事。		不同的是他们不害怕去问别人
to ask -- so you should not be, either! In my interaction design work, for example, I have had to approach ――所以你也应该不害怕！		举个例子，在我进行交互设计时，我回答了很多人关于同一个项目的问题，
multiple folks on the same project to understand how a particular workflow in the software happens, because 比如说这个软件内的工作流到底是怎么样的，这玩意在子系统里面传递，不是所有人都能明白子系统是如何工作的。
it is passed off between a number of subsystems and not every person in the project understands how every subsystem works. 

If you are not sure what to work on, or you are not sure how to get started, or
如果你不确定该干什么，			或者你不确定如何开始，		
you are not sure why that thing someone said in chat is so funny -- ask. It is a
甚至你不确定为什么这事没别人说起来的那么好玩――问。			也许有可能
lot more likely someone is going to tell you that they do not know either, than
很多人会告诉你他们也不知道，						但是这总比
they are going to think that you are stupid. In most cases, you will learn
他们认为你是个傻瓜好。				在大多数情况下，你会学到很多新的东西，
something new that will help make you a better contributor.
这些东西会让你更加进步。

It can be especially effective to seek out a mentor -- some projects even have
找一位导师将会非常有用――一些项目甚至有着指导方案――
mentoring programs -- and ask them if they would not mind being your go-to person when you have questions. 
			在你有问题的时候别忘了去问问他们。

\section*{4. Share and share often. Even if it is not ready yet. Especially if it
is not ready yet.}
	4.不管情况怎么样，经常分享准没错。

We have also noticed new designers in Fedora and other Free and Open Source projects
在Fedora和一些其它的FOSS项目中，我们也注意到，很多新来的设计师在轮到他们展示工作的时候
are a little shy when it comes to showing their work. I understand that you
有点害羞。						我能理解你不想因为一些
do not want to ruin your reputation by putting something out there that is not
不完美或者未完成等原因而收到名誉上的损失，
your best or even finished, but a big part of how Free and Open Source projects
				但是FOSS的宗旨的很大一部分就是频繁的分享和开源。
work is sharing often and openly. 

The further along you have come on a piece before you have shared it, the harder
你分享的越少，越慢，							其他人就会
others will find it to provide you actionable feedback and to jump in and get
越难给你一个反馈或者参与进来。
involved. It is also harder for others to collaborate on your piece themselves
	这也会使得其他人更难与你合作，或者从它身上获得一点成就感，当然也会导致
and feel a sense of ownership for it, supporting and championing it through to
更难的支持与合作。
implementation. In some Free and Open Source projects, not being forthcoming with
		在FOSS项目中，不要被动的接受他人的分享，要主动与他们分享你的各种各样
your sketches, designs, and ideas is even seen as offensive! 
的东西。

Post your ideas, mockups, or designs on the web rather than in email, so it is
把你的想法、模型或者设计什么的放到网上交流，而不是用邮件交流，因为放到网上能够让
easy for others in the project to refer to your asset via copying and pasting the
其他人更加方便的通过复制传播URL（统一资源定位符（URL，英语 Uniform / Universal Resource Locator 的缩写）也被称为网页地址，是因特网上标准的资源的地址（Address)。百度百科http://baike.baidu.com/view/1496.htm）
				来帮你赚点钱。
URL -- especially handy during discussions. The easier it is to find your design
――尤其在讨论时贴出来。			找到你的东西越简单，它被使用的可能
assets, the more likely it is they will be used. 
性越大。

Give this tip a try and keep an open mind. Share your work early and often, and
试一下这个小技巧，也别忘了开源的思想。	早点并且频繁的分享你的工作，并且别忘了把
make your source files available. You might be pleasantly surprised by what
你的源文件放出来。			也许会发生一些让你惊喜的事。
happens!

\section*{5. Be as visible as you can within the project community.}
	5.全方位的开源是很重要的

One tool that -- completely unintentionally -- ended up helping me immensely in
博客――完全是无意间发现的――帮助了我很多，在我开始FOSS项目的时候。
getting started as a FOSS contributor was my blog. I started keeping a
							我坚持写博客，
blog, just for myself, as a sort of rough portfolio of the things I had been
	当然只是个人习惯而已，作为我那一大堆工作的投资组合。
working on. My blog is a huge asset for me, because:
		我的博客对我来说是一笔很大的财富，因为：
\begin{itemize}
 \item As a historical record of project decisions, it is a convenient way to look up old design decisions 	作为项目的历史记录，它可以方便的找出一些老的设计的讨论
-- figure out why we had decided to drop that screen again, or why a particular approach we had tried before 
――比如指出为什么我们决定再次放弃那些东西，或者再项目能正常工作前，我们做过什么。
did not work out, for example.

 \item As a communication device, it helps other contributors associated with your
作为一个通讯设备，它有时能帮助别的相关项目的参与者甚至能让他们知道
project and even users become aware of what work is happening and aware of
项目发生了什么，有一些什么变化等。
upcoming changes in the project. Many times I have missed something essential in a design, and these folks 
					在设计中，有很多次我忘了一些必要的东西，但是一些人的评论总是能让我
have been very quick to post a comment letting me know!
非常迅速的想起来。

 \item It helped me to build my reputation as a FOSS designer, which has helped me build others' trust in my 
它也帮助我建立起作为一个FOSS的设计师的信誉，也建立了别人对我的信任。
design decisions as time has gone on. 

\end{itemize}

Do you blog? Find out which blog aggregations the members of the
你写博客吗？找出你所在的项目的人都在看什么博客，
project you are working on read, and put in requests to have your blog
				然后让他们把你的博客地址加上去（他们通常喜欢
added to them (there is usually a link to do so in the sidebar.) For example, the main blog aggregator you 在博客的边缘加个链接地址。）						举个例子，聚合着所有想要参与Fedora社
will want to join to become a part of the Fedora
区的人的博客叫做Planet Fedora（意思为Fedora星球，地址是http://planet.fedoraproject.org）
community is called Planet Fedora\footnote{\url{http://planet.fedoraproject.org}}. Write a first blog
											现在，尝试着写出
post once you have been added introducing yourself and letting folks know what you like -- all of the sort 你的第一篇博客，让伙伴们知道你在干什么或者你想要干什么吧――所有的信息都在前面提到过哦。
of information advised in tip \#1.

The project will surely have a mailing list or forum where discussion takes
一个项目应该有一个邮件列表或者论坛作为讨论的地点。
place. Join it, and send an intro there too. When you create assets for the
参与进去，别忘了写个介绍。			当你开始工作后――不管你做的东西的大小，
project -- no matter how small, no matter how unfinished -- blog about them,
也不管它是否完成――别忘了在博客上写出来，然后把它上传到项目的维基百科，推特上去
upload them to the project wiki, tweet/dent about them, and send links to
然后把地址发送到聊天室里，然后别忘了收集别人的反馈。
prominent community members on IRC to get their feedback.

Make your work visible, and folks will start to associate you with your work and
让大家都能看到你的工作，这样子伙伴们才会开始和你一起努力，然后帮助你，各种酷酷的项目
approach you with cool projects and other opportunities based solely on that.
都是在这个基础上开始的。


This is everything I wish I had known when first trying to get involved in Free
这5点，就是我希望你决定开始作为一个FOSS的设计师所了解的。
and Open Source software as a designer. If there is any one thing you should
						如果一定要说哪个最重要的话，
take away from this, it is that you should not be shy -- please speak up, please
			那应该是不要害羞――大声讲出来，让别人知道你需要什么，
let your needs be known, please let others know about your talents so they can
			让别人知道你擅长什么以便他们能更好的让你参与FOSS项目中去。
help you apply them to making Free Software rock.
