\chapterwithauthor{Runa Bhattacharjee}{My Project Taught Me how to Grow Up}
					我的项目教会了我如何成长

*					作者介绍
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*
*

\authorbio{For the past 10 years, Runa Bhattacharjee has been translating and working on
	在过去的10年中，Runa Bhattacharjee已经翻译并且本地化了（此处的本地化类似于中国的汉化，就是将软件变成易于被本国用户所接受的样子。）
localizing numerous Open Source projects - ranging from Desktop interfaces to
一大堆的开源项目――从桌面接口到操作系统工具或者介乎两者间的很多很多东西。
Operating System tools and lots of things in between. She strongly believes that
								她坚持认为【一个东西，暂时未发现是什么】					
upstream repositories are the best places to submit any form of changes. She also
是最好的提交修改的地方。						她在Red Hat中
holds a professional portfolio specializing in Localization, at Red Hat. Runa
的本地化领域内拥有非常高的地位。					Runa
translates and maintains translations for Bengali (Indian version), but is
为Bengali（印度版本）进行翻译或者维护翻译，				同时
always happy to help anyone wanting to get started with localization.}
她也热衷于帮助任何想要开始进行本地化工作的人。

\section*{Introduction}
 	简介
Burning the midnight oil has been a favorite form of rebellion by young people
【靠，这句好难理解，字面意思好像不对，先放着】
all over the world. Whether to read a book with a torchlight under the covers or

to watch late night TV reruns or (amongst other things) to hang around on an IRC

channel and tinkering around with an itchy problem with a favorite open source

project. 

\section*{How it all began}
	一切的起因
That is how it all began for me. Let me first write a bit about myself. When I
接下来我将讲诉我是如何开始的。	先让我讲点有关于我自己的。		当我受邀
got introduced to the local Linux Users Group in my city, I was in between jobs
参加我所在城市的Linux用户组的时候，			我正在边工作边考取一个硕士学位。
and studying for a masters degree. Very soon I was a contributor to a few
					很快，我变成了一个项目本地化的参与者，
localization projects and started translating (mostly) desktop interfaces. We
			并且开始翻译（大多数时候）桌面接口。		我们
used a few customized editors with integrated writing methods and fonts. The
使用一些定制的有着完整输出方法和字体的编辑器。				
rendering engines had not matured well enough to display the script with zero

errors on the interfaces, nonetheless we kept on translating. My focus was on

the workflow that I had created for myself. I used to get the translatable
content from the folks who knew how things work, translate it as best as I
could, add in the comments to help the reviewers understand how I comprehended
the text, filled in the necessary information for copyright and credits and sent
them back to the coordinators.

\section*{How it was done}

It was mostly a simple way of doing things. But most importantly it was
\textit{my} independent way of doing things. I took my own time to schedule when
I would work on the translations. These would then be reviewed and returned to
me for changes. Again, I would schedule them for completion as per how I could
squeeze out some time from all the studying and other work that I was doing.
When I did get down to work, I would sit through 9-10 straight hours mostly into
the wee hours of the morning, feeling a high of accomplishment until the next
assignments came through.

\section*{What mattered}

What I did not know was that I played a significant part in the larger scheme of
things. Namely, release schedules. So, when I completed my 2 cents of the task
and sent them over, I did not factor in a situation where they could be rendered
useless because they were too late for the current release and too early for the
next release (which would invariably contain a lot of changes that would require
a rework). Besides these, I was oblivious to the fact how it all mattered to the
entire release process -- integration, packaging, interface testing, bug filing,
resolution.

\section*{How it made me grow up}

All these changed drastically when I moved into a more professional role. So
suddenly I was doing the same thing but in a more structured order. I learned
that the cavalier road-rolling that I had been used to, was not scalable when
one had to juggle through 2-3 release schedules. It had to be meticulously
planned to map with the project roadmaps. While working on translating a desktop
interface, one had to check what the translation schedule was for the main
project. The projected date to start working would be right after when all the
original interface messages had been frozen. Translators could then work
unhindered until the translation deadline, after which they would be marked as
stable in the main repositories and eventually packages would be built. Along
with these schedules, a couple of operating system
distributions would align their schedules as well. So the translators had the
additional responsibility of making sure that the pre-release versions of the
operating system that would be carrying the desktop, went through with some bits
of testing to ensure that the translations made sense on the interface and did
not contain errors.

\section*{What I should have known}
	我应该知道什么
The transition was not easy. Suddenly there was a flood of information that I
had to deal with and additional chores that I had to perform. From being a hobby
and more importantly a stress-buster, suddenly it was serious business. Thinking
in retrospect, I can say that it probably helped me understand the entire
process because I had to learn it from the ground up. And armed with that knowledge
I can analyze situations with a better understanding of all the effective
facets. At the time when I started working on the Open Source project(s) of my
interest, there were much fewer professionals who worked full time in this
domain. Most of the volunteer contributors held day jobs elsewhere and saw these
projects as a way to nurture the creative juices that had dried up in their
routine tasks. So a number of newcomers were never mentored about how to plan
out their projects professionally. They grew to be wonderfully skilled in what
they were doing and eventually figured out how they would like to balance their work
with the rest of the things they were doing.

\section*{Conclusion}
	总结
These days I mentor newcomers and one of the first things that I let them know
is how and in which part of the project they matter. Crafting an individual
style of work is essential as it allows a person a comfortable space to work in,
but an understanding of the organized structure that is affected by their work
imbibes the discipline that is required to hold in check chances of arbitrary
caprice.
